---
title: "a filtering widget for shiny documents"
author: "Tom Greenwood"
date: "11/04/2019"
output: 
 html_document:
  code_folding: show
  css: greenwood-style.css  
  theme: united
  highlight: zenburn
runtime: shiny

---

This is an example of a shiny widget in rmarkdown. It uses the shiny function renderUI, mapped over a selections of column names, to allow the user to first choose which columns to filter on, and then choose which values of those columns should be included in the filter.

Below is the widget function

```{r, message=FALSE, warning=FALSE}


shiny_filters <- function(df) {
  
library(shiny)
library(DT)
library(tidyverse, warn.conflicts = FALSE)
  
# first, we create a vector of all the column names
col_names <- df %>% names

shinyApp(
  
  ui = 
  fluidPage(
    # this input allows the user to choose which columns to filter on
    checkboxGroupInput("filtChoices", "choose filter conditions", choices = col_names),
    # look in the server function to see how this uiOutput is created
    uiOutput("boxes"),
    # ditto above
    DTOutput("dt")

    
  ),
  server = function(input, output, session) {
   # this creates checkboxes for each of the selected filters
   output$boxes <- renderUI({
	  input$filtChoices %>% map(. %>% { expr(checkboxGroupInput(!!., 
    	                                                 !!. , 
    	                                                 choices = df[[!!.]] %>% unique(),
    	                                                 selected = df[[!!.]] %>% unique()
    	                             )) } %>% 
    		         eval )
   })

# then render the summary, based on the filtering conditions
  output$dt <- renderDT({

	validate(need(length(input$filtChoices) != 0, "no filtering conditions selected" ))
	
	tnames <- input$filtChoices 
  snames <- input$filtChoices %>% syms

  filter_expr <- map2(snames, tnames, ~ expr(!!.x %in% input[[!!.y]])) %>%
 	             reduce(~ expr(!!.x & !!.y))

	df %>% filter(!!filter_expr)

	})
}

)
}


```

Then we can use the widget on any data.frame we like, for instance

```{r message=FALSE, warning=FALSE}
shiny_filters(mtcars)
```

Or, alternatively

```{r message=FALSE, warning=FALSE}
shiny_filters(iris)
```



